A sensor grid approach for large scale acoustic monitoring

### 2017-06-19 paper/article.tex
abstract done

\author{Felix Gontier, Mathieu Lagrange, Arnaud Can, Catherine Lavandier}

\address{felix.gontier@reseau.eseo.fr \\ mathieu.lagrange@cnrs.fr}

@@

The acoustic environment represents both societal and environmental concerns, in particular for cities that are subjected to a multitude of noise sources and that count de facto numerous exposed people.

In this context, monitoring the acoustic environnment in urban but also rural or wilderness areas is an important matter. Fostering on the recent development of low cost hardware acoustic sensors, we propose to using a sensor grid approach.

audio sensing

audio encoding

>>>>

\author{F\'elix Gontier, Mathieu Lagrange, Pierre Aumond, Arnaud Can, Catherine Lavandier}

\address{felix.gontier@reseau.eseo.fr}

@@

The acoustic environment represents both societal and environmental concerns. Monitoring the acoustic environnment in urban but also rural or wilderness areas is therefore an important matter. Fostering on the recent development of low cost hardware acoustic sensors, we propose to consider a sensor grid approach to tackle this issue.

In this kind of approach, the crucial question is the nature of the data that is transmitted from the sensors to the processing and archival servers. To this end, we propose an efficient audio coding scheme based on third octave band spectral representation that allows 1) the estimation of most acousitc indicators and 2) the recognition of acoustic events at state of the art performance rate. The former is useful to provide quantitative information about the acoustic environment, while the latter is useful to gather more qualitative information and build perceptually motivated indicators using for example some emergence of a given sound source.

The coding scheme is also demonstrated to transmit spectrally encoded data that, reverted to the time domain using state of the art techniques, is not intelligible, thus protecting the privacy of citizens.
